Blocking-resistant communication\\through domain fronting

### 2014-11-23 docs/meek.tex
spell check

Hiding the endpoint and obscuring byte patterns are important parts of blockinging resistance,
but there are other, more subtle considerations.
We describe what we have done to disguise traffic ``tells'' in \meek,
including using a real web browser to make fronted HTTPS requests
in order to disguise the TLS fingerprint.
We argue that these measures, combined with domain fronting, increase the censor's effort
beyond simple one-shot blocking techniques such as IP address blacklisting, and into
the realm of more expensive, less reliable statistical tests.
\end{abstract}

@@

Domain fronting derives its strength from the
high collateral damage of blocking the fronted-through domain.
To front through \urll{www.google.com} to App Engine, for example,
is to make a bet that the censor will lack the temerity to block Google.
Different censors will differ in their aversion to collateral damage;
blocking an important service is a costly measure
that harms users not involved in circumvention and perhaps a society's economic well-being,
and not all censors can afford to do it.
The Great Firewall of China took the unprecendented step
of blocking all Google services in June 2014~\cite{cn-google-block,cn-google-block-greatfire},
and has since blocked certain CDN domains that were used to host
mirrors of censored web sites, even at the cost of damaging other unrelated sites~\cite{cn-edgecast-block-greatfire}.
In 2012, the government of Pakistan blocked all of YouTube
in order to restrict access to one video,
and in 2011, the government of Egypt briefly completely ``turned off the net.''
% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
These examples show that blocking resistance is not an absolute,
black-and-white security property;
it can only be discussed in an economic context, relative to the costs borne
by the censor and by users of a system.
We can at least roughly quantify the cost of blocking a domain-fronting system:
it is the minimum cost of
blocking the front domain with resultant collateral damage,
conducting a traffic-analysis attack to distinguish
circumvention from ordinary traffic, or
conducting some other unconsidered attack, for example physical surveillance of Internet users.
As long as all these costs are high,
domain fronting is difficult to block.

>>>>

Hiding the endpoint and obscuring byte patterns are important parts of blocking resistance,
but there are other, more subtle considerations.
We describe what we have done to disguise traffic ``tells'' in \meek,
including using a real web browser to make fronted HTTPS requests
in order to disguise the TLS fingerprint.
We argue that these measures, combined with domain fronting, increase the censor's effort
beyond simple one-shot blocking techniques such as IP address blacklisting, and into
the realm of more expensive, less reliable statistical tests.
\end{abstract}

@@

Domain fronting derives its strength from the
high collateral damage of blocking the fronted-through domain.
To front through \urll{www.google.com} to App Engine, for example,
is to make a bet that the censor will lack the temerity to block Google.
Different censors will differ in their aversion to collateral damage;
blocking an important service is a costly measure
that harms users not involved in circumvention and perhaps a society's economic well-being,
and not all censors can afford to do it.
The Great Firewall of China took the unprecedented step
of blocking all Google services in June 2014~\cite{cn-google-block,cn-google-block-greatfire},
and has since blocked certain CDN domains that were used to host
mirrors of censored web sites, even at the cost of damaging other unrelated sites~\cite{cn-edgecast-block-greatfire}.
In 2012, the government of Pakistan blocked all of YouTube
in order to restrict access to one video,
and in 2011, the government of Egypt briefly completely ``turned off the net.''
% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
These examples show that blocking resistance is not an absolute,
black-and-white security property;
it can only be discussed in an economic context, relative to the costs borne
by the censor and by users of a system.
We can at least roughly quantify the cost of blocking a domain-fronting system:
it is the minimum cost of
blocking the front domain with resultant collateral damage,
conducting a traffic-analysis attack to distinguish
circumvention from ordinary traffic, or
conducting some other unconsidered attack, for example physical surveillance of Internet users.
As long as all these costs are high,
domain fronting is difficult to block.
